### 2014-02-25 paper/retrofit.tex
Fix erase.

\begin{figure}
\begin{align*}
  &|erase il (iconf iS its) =
  iconf (erase il iS) (fltr (\ it . it = bullet) (map (erasef il) its))| \\
  &|erase il (tconf id il' ie) =| \begin{cases}
    %|lconf bullet bullet bullet bullet| & |il' cantFlowTo il| \\
    |bullet| & |il' cantFlowTo il| \\
    |fullconf id il' (erase il tS) (erase il ie)| & \text{otherwise}
  \end{cases} \\
  %&|erase il iS [i mapsto Q] = iS [i mapsto (erase il Q)]|\\
  &|erase il Q = filter il Q|\\
  &|erase il (send id il' ie) =| \begin{cases}
    |send id il' bullet| & |il' cantFlowTo il| \\
    |send id il' (erase il ie)| & \text{otherwise}
  \end{cases} \\
  &\text{In all other cases, |erasef il| is applied homomorphically.}
\end{align*}
\caption{Erasure function.}
\end{figure}

>>>>

\begin{figure}
\begin{align*}
  &|erase il (iconf iS its) =
  iconf (erase il iS) (fltr (\ it . it = bullet) (map (erasef il) its))| \\
  &|erase il (tconf id il' ie) =| \begin{cases}
    %|lconf bullet bullet bullet bullet| & |il' cantFlowTo il| \\
    |bullet| & |il' cantFlowTo il| \\
    |tconf id il' ie| & \text{otherwise}
  \end{cases} \\
  %&|erase il iS [i mapsto Q] = iS [i mapsto (erase il Q)]|\\
  &|erase il Q = filter il Q|\\
  &\text{In all other cases, |erasef il| is applied homomorphically.}
\end{align*}
\caption{Erasure function.}
\end{figure}
